Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2020-08-12 docs/00-manuscripts/ieee/ieee-manuscript.tex
Apply suggestions from code review

The airborne hyperspectral data was acquired during two flight campaigns which took at noon on September 28th and October 5th 2016.
The images were taken by an AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

The idea of splitting the features into different sets originated from the question whether feature-engineered indices from reflectance values have a positive effect on model performance, as for example demonstrated by \cite{pena2017} within a spectro-temporal setting.
% JM: just a little reminder to avoid sentences where the main verb appears long after the sentence has started
Benchmarking learners on these feature sets while keeping all other variables such as model type, tuning strategy and partitioning method constant makes it possible to draw conclusions on their individual impact.
However, rather than only looking at these three groups also combinations of such were taken into account:

@@

A potential limiting factor in this study could be the upper limit of 600 iterations used for the XGBoost algorithm (hyperparameter \texttt{nrounds}), especially for feature sets including NRIs (\autoref{tab:hyperparameter_limits}).
This setting was a compromise between runtime and tuning space extension with the goal to work well for most feature sets.
It may be recommendable to increase this upper limit to a value closer to the number of features in the dataset in order to be able to exploit the full range of this hyperparameter.

@@

One objective of ths study was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result}, no overall positive or negative trend was found for all models that related to specific feature sets.
The performance of RF and XGBoost on the VI feature set was about six percentage points lower than on others.
One reason could be the lack of coverage in the wavelength area between 810 nm and 1000 nm (\autoref{fig:fi-permut-vi-hr}).
In addition, for all learners but SVM a better performance was observed when NRI indices were included in the feature set (i.e. NRI-VI, HR-NRI, HR-NRI-VI).

>>>>

The airborne hyperspectral data was acquired during two flight campaigns which took place at noon on September 28th and October 5th 2016.
The images were taken by an AISAEAGLE-II sensor.
All preprocessing steps (geometric, radiometric, atmospheric) were conducted by the \ac{ICGC}.
The first four bands were corrupted, leaving 122 bands with valid information.
Additional metadata information is available in \autoref{tab:hyperparameter_metadata}.

@@

The idea of splitting the features into different sets originated from the question whether feature-engineered indices derived from reflectance values have a positive effect on model performance.
\cite{pena2017} is an exemplary study which used this approach in a spectro-temporal setting.
% JM: just a little reminder to avoid sentences where the main verb appears long after the sentence has started
Benchmarking learners on these feature sets while keeping all other variables such as model type, tuning strategy and partitioning method constant makes it possible to draw conclusions on their individual impact.
However, rather than only looking at these three groups also combinations of such were taken into account:

@@

A potential limiting factor in this study could be the upper limit of 600 iterations used for the XGBoost algorithm (hyperparameter \texttt{nrounds}), especially for feature sets including NRIs (\autoref{tab:hyperparameter_limits}).
This setting was a compromise between runtime and tuning space extension with the goal to work well for most feature sets.
It may be recommendable to increase this upper limit to a value closer to the number of features in the dataset in order to be able to exploit the full potential of this hyperparameter.

@@

One objective of this study was whether expert-based or data-driven feature engineering has a positive influence on model performance.
With respect to \autoref{fig:perf-result}, no overall positive or negative trend was found for all models that related to specific feature sets.
The performance of RF and XGBoost on the VI feature set was about six percentage points lower than on others.
One reason could be the lack of coverage in the wavelength area between 810 nm and 1000 nm (\autoref{fig:fi-permut-vi-hr}).
In addition, for all learners but SVM a better performance was observed when NRI indices were included in the feature set (i.e. NRI-VI, HR-NRI, HR-NRI-VI).
